Left-linear rules in adhesive categories

### 2024-02-10 icalp/fusione.tex
minor things

The correspondence between sequential independence and switchability
is fundamental.  A very large class of DPO rewriting systems - in the
line of \cite{baldan2011adhesivity} - can be identified where all
independence pairs are good for left-linear rewriting systems: ses
\Cref{app:fill}.

>>>>

The correspondence between sequential independence and switchability
is fundamental.  A very large class of DPO rewriting systems - in the
line of \cite{baldan2011adhesivity} - can be identified where all
independence pairs are good for left-linear rewriting systems. The details are in 
\Cref{app:fill}. Here it is important only to observe that such class includes $\cat{Set}$ and it is closed by comma and functor category constructions. As such it includes essentially all categories (e.g., presheaves over set) which are typically considered for modelling purposes.
